Compositional equivalences based on Open pNets

### 2021-08-30 2016-Weak-FH-Bisim/WeakBisim.tex
substitutions redefined

We denote $y\gets e$ a substitution~. The application of the substitution is denoted
$\subst{y\gets e}$, the operation replaces in a term all occurrences 
of the variable $y$ by the expression $e$. 
$\Post$ ranges over (indexed) sets of substitutions; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner. $\otimes$ is the composition operator on substitutions, such that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post'})\subst{\Post}$.

For this property to be valid when the substitution does not operate on all variables,
we define the composition operation as follows: 
%\TODO{version d eric reprise et corrigee}
%$(x_k\gets e_k)^{k\in K}\shortotimes \Post =  (x_k\gets e_k\subst{\Post})^{k\in K}$
%\ERIC{J'ai un probleme ici... quand $Post'$ agit sur des vars de $t$ qui ne sont pas substitutees par $Post$, alors les 2 defs de $\shortotimes$ ci-dessus ne sont pas equivalentes:}\\
%$F(x,z)(\subst{x\gets z}\shortotimes\subst{z\gets 1})=F(x,z)(\subst{x\gets 1})=F(1,z)$\\
%\ERIC{Alors que}\\
%$(F(x,z)\subst{x\gets z})\subst{z\gets 1})=F(z,z)\subst{z\gets 1}=F(1,1)$
%
%\ERIC{Une definition plus correcte serait peut-etre:}\\

>>>>

This article also uses substitutions. Applying a substitution inside a term $t$ is denoted $t\subst{y_i\gets e_i}^{i\in I}$ and consists in replacing in parallel all the occurrences of variables $y_i$ in the term $t$ by the terms $e_i$. Note that a substitution is defined by a partial function that is applied on the variables inside a term. We let $\Post$ range over partial functions that are used as substitution and use the notation $\{y_i\gets e_i\}^{i\in I}$ to define such a partial function\footnote{Note that the fact that substitutions are defined from partial function  implies that each $y_i$ is different.}.
 $\subst{\Post}$ is thus the operation that applies,  in a parallel manner,  the substitution defined by the partial function $\Post$. $\otimes$ is a composition operator on these partial functions, such that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post'})\subst{\Post}$.
This property must also be valid when the substitution does not operate on all variables.
We thus define the composition operation as follows: 
%\TODO{version d eric reprise et corrigee}
%$(x_k\gets e_k)^{k\in K}\shortotimes \Post =  (x_k\gets e_k\subst{\Post})^{k\in K}$
%\ERIC{J'ai un probleme ici... quand $Post'$ agit sur des vars de $t$ qui ne sont pas substitutees par $Post$, alors les 2 defs de $\shortotimes$ ci-dessus ne sont pas equivalentes:}\\
%$F(x,z)(\subst{x\gets z}\shortotimes\subst{z\gets 1})=F(x,z)(\subst{x\gets 1})=F(1,z)$\\
%\ERIC{Alors que}\\
%$(F(x,z)\subst{x\gets z})\subst{z\gets 1})=F(z,z)\subst{z\gets 1}=F(1,1)$
%
%\ERIC{Une definition plus correcte serait peut-etre:}\\
